---
title: "Exp6 Analysis"
author: "Mrudula"
date: "`r format(Sys.time(), '%d %B,%Y')`"
output: html_document
---

**This document contains the result memo of Experiment 6 aimed to explore overshadowing in a CL paradigm. It builds on from the design used in Experiment 5 that showed success in manipulating saliency. HEnce, this experiment goes back to exploring overshadowing in depth by introducing learn and test trials with a 90:10 and 80:20 contingency ratio. In this design the target position is no longer dependent on the letters and is presented centrally. The task also is now changed to odd/even instead of 5 and 8.**


Loading the relevant libraries and the dataset

```{r loadlibs, include=FALSE, message=FALSE}

library(tidyverse)
library(plyr)
library(ez)
library(schoRsch)
library(knitr)
library(pander)
library(rmarkdown)
library(reshape2)
library(here)
library(ggpubr)
library(lme4)
library(nlme)

#set_here()

Exp6data <- read.csv(here("Data", "Exp6_fulldataset.csv"))
Exp6data$participant <- as.factor(Exp6data$participant)

```

### Data preparation and cleaning

  - Removing unnecessary columns
  - Preparing the RT trial 
  - Creating a column for Accuracy and Error Rate

```{r cleaning, include=FALSE, message=FALSE}
#removing unnecessary columns
Exp6data <- Exp6data %>%
  select(-X,-ConsentKey.keys,-ConsentKey.rt,-Begin.keys,-Begin.rt,-checkresp.corr,-checkresp.keys,-checkresp.rt,-Attention.thisRepN,-Attention.thisTrialN,-Attention.thisN,-Attention.thisIndex,-Attention.ran,-AttnQuestion,-AttnAnswer,-NextStep.keys,-NextStep.rt,-InstRep.ran,-InstRep.thisN,-InstRep.thisTrialN,-InstRep.thisRepN,-InstRep.thisIndex,-PracProceed.keys,-PracProceed.rt,-Prac_loop.thisRepN,-Prac_loop.thisTrialN,-Prac_loop.thisN,-Prac_loop.thisIndex,-Prac_loop.ran,-Exp_proceed.keys,-Exp_proceed.rt,-PracRepeat.ran,-PracRepeat.thisRepN,-PracRepeat.thisN,-PracRepeat.thisIndex,-PracRepeat.thisTrialN,-brkContinue.keys,-PauseResp.keys,-PauseResp.rt,-CAtrials.thisRepN,-CAtrials.ran,-CAtrials.thisTrialN,-CAtrials.thisIndex, -CA_Proceed.keys,-CA_Proceed.rt,-headstartLearn.thisRepN,-headstartLearn.thisTrialN,-headstartLearn.thisIndex,-headstartLearn.thisN,-headstartLearn.ran,-ExpTrials.ran,-ExpTrials.thisIndex,-CA_trials.thisRepN,-CA_trials.thisN,-CA_trials.thisIndex,-CA_trials.thisTrialN,-CA_trials.ran,-AwareQ_loop.thisRepN,-AwareQ_loop.ran,-AwareQ_loop.thisIndex,-AwareQ_loop.thisTrialN,-todebrief.keys,-Finalend.keys)


Exp6data <- Exp6data%>%group_by(participant)%>%fill(Screen_bg,.direction = "down")

Exp6data <- Exp6data %>%
  mutate(BlockCount = ifelse(ExpTrials.thisN <= 93, 1,
                             ifelse(ExpTrials.thisN <=187 & ExpTrials.thisN > 93,2,
                                    ifelse(ExpTrials.thisN <= 271 & ExpTrials.thisN > 187,3,
                                           ifelse(ExpTrials.thisN <= 375 & ExpTrials.thisN > 271,4,NA)))))


#adjusting RT
Exp6data <- separate(Exp6data, col = TargetResp.rt, into = c("RT_Trials", "RT_secondary"), sep = ',')
Exp6data$RT_Trials <- Exp6data$RT_Trials%>%
  str_replace_all("\\[|\\]","")%>%
  as.double(Exp6data$RT_Trials)
Exp6data$RT_Trials <- 1000*(Exp6data$RT_Trials)

###creating a separate df with the contingency awareness
Exp6_CA <- Exp6data%>%
 filter(Block == "ContingencyCheck" | str_detect(AwareQ, "Press"))
Exp6data <- Exp6data%>%drop_na(RT_Trials)

Exp6data$ACC_trials <- Exp6data$TargetResp.corr
Exp6data$ErrorRate <- 1 - Exp6data$ACC_trials

##exploratory removing participants with average performance
`%notin%` <- Negate(`%in%`)




```


### Descriptives

Summary of the overall Reaction Time, accuracy and Error Rate

```{r descriptives, echo=FALSE}
pander(summary(Exp6data$RT_Trials), style = 'rmarkdown',caption = 'Mean RT')
pander(table(Exp6data$ACC_trials),style = 'rmarkdown',caption = "Accuracy")

pander(round(table(Exp6data$ACC_trials)/nrow(Exp6data)*100, digits = 3), style = 'rmarkdown', caption = "Percentage of errors")
```

Removing the outliers and farouts

```{r exclusions, echo=FALSE}
Exp6data$RT_Trials[Exp6data$ACC_trials==0] <- NA


#creating function to remove the outliers and farouts
computeTukeys <- function(x){
  P25 <- quantile(x$RT_Trials, .25, na.rm = TRUE, type = 6) #type = 6 -> used in SPSS
  P75 <- quantile(x$RT_Trials, .75, na.rm = TRUE, type = 6)
  x$Outlier <- P75 + 1.5*(P75 - P25)
  x$Farouts <- P75 + 3.0*(P75 - P25)
  return(x)
}


#identifying the outliers and farouts at individual level
Exp6data <- ddply(Exp6data, .(participant), computeTukeys)

#creating new column with RT trials after removing outliers/farouts
Exp6data$RT_ifo <- Exp6data$RT_Trials
Exp6data$RT_io <- Exp6data$RT_Trials

Exp6data$RT_ifo[Exp6data$RT_ifo > Exp6data$Farouts|Exp6data$RT_ifo < 300] <- NA

Exp6data$RT_io[Exp6data$RT_io > Exp6data$Outlier|Exp6data$RT_io < 300] <- NA


pander(summary(Exp6data$RT_ifo), style = 'rmarkdown', caption = "Summary of RT after removing Farouts")
pander(summary(Exp6data$RT_io), style = 'rmarkdown', caption = "Summary of RT after removing Outliers")

```
## Computing BIS

```{r}
Exp6data$AccuracyRate <- 1-Exp6data$ErrorRate
BIS <- function(x) {
  n <- length(x$group)    # sample size to correct var()-function result (which uses n-1)
  srt <- sqrt( ((n-1)/n) * var(x$RT_Trials) )     # sample standard deviation across all rts
  spc <- sqrt( ((n-1)/n) * var(x$AccuracyRate) )            # sample standard deviation across all rts
  mrt <- mean(x$RT_Trials)                        # mean across all rts
  mpc <- mean(x$AccuracyRate)                               # mean across all pcs
  zrt <- (x$RT_Trials)/srt                    # standardized rts
  zpc <- (x$AccuracyRate-mpc)/spc                           # z-standardized pcs
  x$bis <- zpc - zrt                              # Balanced Integration Score
  
  return(x)                                       # return x.frame with added variable 'bis'
}


Exp6data <-  BIS(Exp6data)

```

## ANALYSES

### 1. Validity Manipulation check - Learn trials

Valid trials are significantly faster than invalid trials with a mean difference of 17ms (farouts) and 17ms for outliers.

```{r valcheck, echo=FALSE,message=FALSE}
##creating a data set with just learn trials
Exp6learn_agg <- aggregate(data = Exp6data, RT_ifo~participant+Validity,mean)
Exp6learn_agg_o <- aggregate(data = Exp6data, RT_io~participant+Validity,mean)

#for farouts
pander(aggregate(data = Exp6learn_agg, RT_ifo~Validity,mean), style = "rmarkdown", caption = "Table containing means of valid and invalid learn trials, farouts excluded")


pander((t.test(data = Exp6learn_agg, RT_ifo~Validity,paired = TRUE)), style = 'rmarkdown', caption = "t test showing differences between valid and invalid trials")



#for outliers
pander(aggregate(data = Exp6learn_agg_o, RT_io~Validity,mean), style = "rmarkdown", caption = "Table containing means of valid and invalid learn trials, outliers excluded")


pander((t.test(data = Exp6learn_agg_o, RT_io~Validity,paired = TRUE)), style = 'rmarkdown', caption = "t test showing differences between valid and invalid trials-excluding outliers")


```

### 2. Saliency Manipulation Check 

This analysis checks whether the saliency manipulation worked by comapring the RT between trials where the number appeared in salient letters position vs non salient letter's position.

      1. Farouts: It is almost significant(t > 1, p = 0.12) with a the mean difference is 17ms. 
      2. Outliers: It is significant with a mean difference of 22ms
```{r salcheck, echo=FALSE, message=FALSE}
Exp6SalCheck <- aggregate(data = Exp6data, RT_ifo~participant+Saliency, subset = (Block == "SalMC"), mean)
Exp6SalCheck_o <- aggregate(data = Exp6data, RT_io~participant+Saliency, subset = (Block == "SalMC"), mean)


pander(t.test(RT_ifo~Saliency, data = Exp6SalCheck,paired=TRUE),style = "rmarkdown", caption = "t test result for saliency manipulation")

pander(t.test(RT_io~Saliency, data = Exp6SalCheck_o,paired=TRUE),style = "rmarkdown", caption = "t test result for saliency manipulation, outliers")
```

### 3. Interaction of Validity x Saliency in test trials

This analysis is the main one concerning overshadowing. 

     1. Farouts:
     The Validity effect is close to significance (p = 0.07) and F value = 3.3. The interaction however is not significant. The plot shows a trend which is in the expected direction. Numerically, the validity effect for salient trials is 11.5 ms and for non salient is 5.5ms.  probably it is just the case that overshadowing is not strong enough to be picked up by the participants in a learn-test intermixed paradigm to make it statistically significant.

     

```{r interactionfo, echo=FALSE, warning=FALSE, message=FALSE}


## aggregating the data for farouts and for outliers

Exp6agg_fo <- aggregate(data = Exp6data, RT_ifo~participant+Validity+Saliency, subset = (Condition == "test"), mean)

# aggsd <- aggregate(data = Exp6data, RT_ifo~participant+Validity+Saliency, subset = (Condition == "test"), sd)
# names(aggsd)[names(aggsd) == "RT_ifo"] <- "SD"
# 
# Exp6agg_fo <- merge(Exp6agg_fo,aggsd)
# Exp6agg_fo$RT_SD <- Exp6data %>%
#   group_by(participant,Validity,Saliency)%>%
#   filter(Condition == "test")%>%
#   sd(Exp6data$RT_ifo)
# 
# summary(Exp6agg_fo$RT_ifo)
# Exp6agg_fo<- Exp6agg_fo%>%mutate(Zself = ((mean(Exp6data$RT_ifo))-RT_ifo)/SD)
# Exp6agg_fo$ZRT <- scale(Exp6agg_fo$RT_ifo)
# 
# Exp6data$ZRTfull <- Exp6data %>%scale(Exp6data$RT_ifo)
  
Exp6agg_o <- aggregate(data = Exp6data, RT_io~participant+Validity+Saliency, subset = (Condition == "test"), mean)


anova_VS_fo <- ezANOVA(data = Exp6agg_fo,
                       dv = RT_ifo,
                       wid = participant,
                       within = .(Validity, Saliency),type = 3,
                       detailed = TRUE)
panderOptions('table.split.table',300)
pander(anova_VS_fo, style = "rmarkdown", caption = "ANOVA for test trials with Validity and Saliency as factors",split.table = Inf, missing = NA)

# aov_VS_fo <- aov(RT_ifo~(Validity*Saliency)+Error(participant/(Validity*Saliency)), data = Exp6agg_fo)
# summary(aov_VS_fo)

ezPlot(data = Exp6agg_fo,
        dv = RT_ifo,
        wid = participant,
        within = .(Validity, Saliency),
       split = Validity, x = Saliency, do_bars = FALSE)+theme_classic()+
  ylim(500,600)+
  ggtitle("Interaction effect between saliency and validity for test trials")



#stdInteraction_fo <- ggplot(Exp6agg_fo, aes(x=Saliency, y=RT_ifo,color = Validity))+
#    geom_line(aes(group = Validity, linetype = Validity),size = 1,stat = "summary", fun = "mean",)+
#    geom_point(stat = "summary", fun = "mean", aes(shape = Validity))+ylim(500,600)+
#  scale_color_manual(values = c("deepskyblue4","cadetblue3"))+
#  theme_classic()+ylab("ReactionTime (in ms)")+ggtitle("Interaction of Validity and Saliency")

#ggsave(filename = here("Figures","interaction_fo.png"),stdInteraction_fo)

mean_valEffect_fo <- ezStats(data = Exp6agg_fo,
        dv = RT_ifo,
        wid = participant,
        within_full = .(Saliency,Validity),
        within = .(Saliency),
        diff=.(Validity),
        reverse_diff = TRUE)

pander(mean_valEffect_fo, style = "rmarkdown", title = "Validity effect(invalid-valid) for salient and non salient letters in test trials(farouts)")


pander(t.test(data = Exp6agg_fo, RT_ifo~Validity, subset = (Saliency == "Salient"), paired = TRUE), style = "rmarkdown", caption = "t test for validity effect for salient trials, farouts")
```

     2. Outliers:
     The validity effect is very strong (p <.001) with F value = 12.35.The interaction is again not significant and like the farouts analysis the plot seems to look promising- salient trials have a validity effect of 13.6ms whereas non salient trials have an effect of 9.3ms. 
     

```{r interactiono, echo=FALSE, warning=FALSE, message=FALSE}
##for outliers
anova_VS_o <- ezANOVA(data = Exp6agg_o,
                       dv = RT_io,
                       wid = participant,
                       within = .(Validity, Saliency),
                       detailed = TRUE)
panderOptions('table.split.table',300)
pander(anova_VS_o, style = "rmarkdown", caption = "ANOVA for test trials(w/o outliers) with Validity and Saliency as factors",split.table = Inf, missing = NA)


ezPlot(data = Exp6agg_o,
        dv = RT_io,
        wid = participant,
        within = .(Validity, Saliency),
       split = Validity, x = Saliency, do_bars = FALSE)+theme_classic()+ylim(500,600)+ggtitle("interaction effect between saliency and validity for test trials without outliers")

# stdInteraction_o <- ggplot(Exp6agg_o, aes(x=Saliency, y=RT_io,color = Validity))+
#     geom_line(aes(group = Validity, linetype = Validity),size = 1,stat = "summary", fun = "mean",)+
#     geom_point(stat = "summary", fun = "mean", aes(shape = Validity))+ylim(500,600)+
#   scale_color_manual(values = c("deepskyblue4","cadetblue3"))+
#   theme_classic()+ylab("ReactionTime (in ms)")+ggtitle("Interaction of Validity and Saliency")

#ggsave(filename = here("Figures","interaction_o.png"),stdInteraction_o,width = 6,height = 4)

  mean_valEffect_o <- ezStats(data = Exp6agg_o,
        dv = RT_io,
        wid = participant,
        within_full = .(Saliency,Validity),
        within = .(Saliency),
        diff=.(Validity),
        reverse_diff = TRUE)

pander(mean_valEffect_o, style = "rmarkdown", title = "Validity effect(invalid-valid) for salient and non salient test trials(outliers)")



pander(t.test(data = Exp6agg_o, RT_io~Validity, subset = (Saliency == "Salient"), paired = TRUE), style = "rmarkdown", caption = "t test for validity effect for salient trials, outliers")

```




Plots to show these effects. 

```{r valeffect plot, echo=FALSE,message=FALSE,warning=FALSE}

Valeffectplot_fo <- ggplot(mean_valEffect_fo, aes(x=Saliency, y=Mean,fill = Saliency))+
    geom_bar(stat = "identity")+
  scale_fill_manual(values = c("cadetblue3","deepskyblue4"))+ylim(0,15)+
  theme_classic()+ylab("Validity effect (in ms)")+ggtitle("Difference between invalid and valid trials")
Valeffectplot_fo
#ggsave(filename = here("Figures","Valeffectplot_fo.png"),Valeffectplot_fo,width = 6, height = 4)


##for outliers

Valeffectplot <- ggplot(mean_valEffect_o, aes(x=Saliency, y=Mean,fill = Saliency))+
    geom_bar(stat = "identity")+
  scale_fill_manual(values = c("cadetblue3","deepskyblue4"))+ylim(0,15)+
  theme_classic()+ylab("Validity effect (invalid - valid trials) in ms")+ggtitle("Difference between invalid and valid trials")
Valeffectplot
#ggsave(filename = here("Figures","Valeffectplot_o.png"),Valeffectplot,width = 6, height = 4)
```



### 4. Error Rate

The Error Rate analysis shows the exact expected trend where the difference in error rate is highest when the trials are salient letters compared to when they are non salient. Both the main effects of Validity and Saliency are significant and the interaction is also significant. 

Maybe this could throw more light on expected associations and quick responses leading to errors - can it be concluded that learning and overshadowing was successful based on error rates??

```{r Errorate, echo=FALSE, message=FALSE, warning=FALSE}

Exp6agg_ER <- aggregate(data = Exp6data,ErrorRate~participant+Validity+Saliency,subset = (Condition == "test"),mean)

Exp6ER <- aggregate(data = Exp6data,ErrorRate~participant,mean)
boxplot(Exp6ER$ErrorRate)

anova_t_ER <- ezANOVA(data = Exp6agg_ER,
        dv = ErrorRate,
        wid = participant,
        within = .(Saliency,Validity),
        detailed = TRUE)
panderOptions('table.split.table',300)
pander(anova_t_ER, style = 'rmarkdown', caption = "ANOVA results: ErrorRates in test trials", split.table = "Inf", missing = NA)

ezPlot(data = Exp6agg_ER,
        dv = ErrorRate,
        wid = participant,
        within = .(Saliency,Validity),
       split = Validity, x = Saliency, do_bars = FALSE)+theme_classic()+ylim(0,0.15)+
  ggtitle("Error rate among test trials")


errorrateplot <-  ggplot(Exp6agg_ER, aes(x=Saliency, y=ErrorRate,color = Validity))+
    geom_line(aes(group = Validity, linetype = Validity),size = 1,stat = "summary", fun = "mean",)+
    geom_point(stat = "summary", fun = "mean", aes(shape = Validity))+
  scale_color_manual(values = c("deepskyblue4","cadetblue3"))+ylim(0,0.15)+
  theme_classic()+ylab("Error Rate")+ggtitle("Interaction of Validity and Saliency with ErrorRate as DV")

#ggsave(filename = here("Figures","ErrorRate.png"),errorrateplot,width=6,height = 4)
```


### 5. Inverse Efficiency scores

```{r}
## create a df that contains both Errorrate and RT

Exp6test <- Exp6data %>%
  subset(Condition == "test")

Exp6agg_IES <- aggregate(Exp6test[,c("RT_ifo","ErrorRate")], by = list(participant = Exp6test$participant,
                                                                       Validity = Exp6test$Validity,
                                                                       Saliency = Exp6test$Saliency), mean,na.rm = TRUE)

Exp6agg_IES$IES <- Exp6agg_IES$RT_ifo/(1-Exp6agg_IES$ErrorRate)
Exp6agg_IES$ZRT <- scale(Exp6agg_IES$RT_ifo)
Exp6agg_IES$PC <- 1-Exp6agg_IES$ErrorRate
Exp6agg_IES$ZPC <- scale(Exp6agg_IES$PC)
Exp6agg_IES$BIS <- Exp6agg_IES$PC - Exp6agg_IES$ZRT

anova_t_IES <- ezANOVA(data = Exp6agg_IES,
        dv = IES,
        wid = participant,
        within = .(Saliency,Validity),
        detailed = TRUE)
panderOptions('table.split.table',300)
pander(anova_t_IES, style = 'rmarkdown', caption = "ANOVA results: using IES", split.table = "Inf", missing = NA)

ezPlot(data = Exp6agg_IES,
        dv = IES,
        wid = participant,
        within = .(Saliency,Validity),
       split = Validity, x = Saliency, do_bars = FALSE)+theme_classic()+ylim(600,700)+
  ggtitle("Interaction effect with IES plotted on the y axis")

IESinterplot <- ggplot(Exp6agg_IES, aes(x=Saliency, y=IES,color = Validity))+
    geom_line(aes(group = Validity, linetype = Validity),size = 1,stat = "summary", fun = "mean",)+
    geom_point(stat = "summary", fun = "mean", aes(shape = Validity))+ylim(500,600)+
  scale_color_manual(values = c("deepskyblue4","cadetblue3"))+
  theme_classic()+ylab("IES (in ms)")+ggtitle("Interaction of Validity and Saliency")
#ggsave(filename = here("Figures","IESinterplot_fo.png"),IESinterplot)

meanIES <- ezStats(data = Exp6agg_IES,
        dv = IES,
        wid = participant,
        within_full = .(Saliency,Validity),
        within = .(Saliency),
        diff = .(Validity),
        reverse_diff = TRUE)

pander(meanIES, style = "rmarkdown", caption = "Mean IES score validity effect")

ggplot(data = meanIES, aes(x = Saliency, y = Mean, fill = Saliency))+scale_fill_manual(values = c("cadetblue3","deepskyblue4"))+
  geom_bar(stat = "identity")+
  theme_classic()+
  ylab("Validity Effect(in ms)")+theme(legend.title = element_blank())+
  ggtitle("Validity Effect (invalid - valid) across test trials (IES) averaged across participant")

## with BIS

anova_t_BIS <- ezANOVA(data = Exp6agg_IES,
        dv = BIS,
        wid = participant,
        within = .(Saliency,Validity),
        detailed = TRUE)
panderOptions('table.split.table',300)
pander(anova_t_BIS, style = 'rmarkdown', caption = "ANOVA results: using IES", split.table = "Inf", missing = NA)

ezPlot(data = Exp6agg_IES,
        dv = BIS,
        wid = participant,
        within = .(Saliency,Validity),
       split = Validity, x = Saliency, do_bars = FALSE)+theme_classic()+
  ggtitle("Interaction effect with BIS plotted on the y axis")


###FOR OUTLIERS

Exp6agg_IES_o <- aggregate(Exp6test[,c("RT_io","ErrorRate")], by = list(participant = Exp6test$participant,
                                                                       Validity = Exp6test$Validity,
                                                                       Saliency = Exp6test$Saliency), mean,na.rm = TRUE)

Exp6agg_IES_o$IES <- Exp6agg_IES_o$RT_io/(1-Exp6agg_IES_o$ErrorRate)

anova_t_IES_o <- ezANOVA(data = Exp6agg_IES_o,
        dv = IES,
        wid = participant,
        within = .(Saliency,Validity),
        detailed = TRUE)
panderOptions('table.split.table',300)
pander(anova_t_IES_o, style = 'rmarkdown', caption = "ANOVA results: using IES(outliers)", split.table = "Inf", missing = NA)

anova_out(anova_t_IES_o)
ezPlot(data = Exp6agg_IES_o,
        dv = IES,
        wid = participant,
        within = .(Saliency,Validity),
       split = Validity, x = Saliency, do_bars = FALSE)+theme_classic()+
  ggtitle("Interaction effect with IES plotted on the y axis")

IESinterplot_o <- ggplot(Exp6agg_IES_o, aes(x=Saliency, y=IES,color = Validity))+
    geom_line(aes(group = Validity, linetype = Validity),size = 1,stat = "summary", fun = "mean",)+
    geom_point(stat = "summary", fun = "mean", aes(shape = Validity))+
  scale_color_manual(values = c("deepskyblue4","cadetblue3"))+ylim(550,650)+
  theme_classic()+ylab("IES (in ms)")+ggtitle("Interaction of Validity and Saliency")
#ggsave(filename = here("Figures","IESinterplot_o.png"),IESinterplot_o)

meanIES_o <- ezStats(data = Exp6agg_IES,
        dv = IES,
        wid = participant,
        within_full = .(Saliency,Validity),
        within = .(Saliency),
        diff = .(Validity),
        reverse_diff = TRUE)

pander(meanIES_o, style = "rmarkdown", caption = "Mean IES score validity effect")

valeffectIES_o <- ggplot(data = meanIES_o, aes(x = Saliency, y = Mean, fill = Saliency))+scale_fill_manual(values = c("cadetblue3","deepskyblue4"))+
  geom_bar(stat = "identity")+
  theme_classic()+
  ylab("Validity Effect(invalid-valid trials) in ms")+theme(legend.title = element_blank())+
  ggtitle("Validity Effect (invalid - valid) across test trials (IES) averaged across participant")
valeffectIES_o
#ggsave(filename = here("Figures","valEffectwithIES_o.png"),valeffectIES_o)
```

Now while computing just the validity effect for each and checking if they are significant 

```{r}
pander(t.test(data = Exp6agg_IES, IES~Validity, subset = (Saliency == "Salient"), paired = TRUE), style = "rmarkdown", caption = "t. test result of validity effect for salient trials")

pander(t.test(data = Exp6agg_IES, IES~Validity, subset = (Saliency == "NonSalient"), paired = TRUE), style = "rmarkdown", caption = "t. test result of validity effect for nonsalient trials")

pander(t.test(data = Exp6agg_IES_o, IES~Validity, subset = (Saliency == "Salient"), paired = TRUE), style = "rmarkdown", caption = "Outlier:t. test result of validity effect for salient trials")

pander(t.test(data = Exp6agg_IES_o, IES~Validity, subset = (Saliency == "NonSalient"), paired = TRUE), style = "rmarkdown", caption = "OUtlier:t. test result of validity effect for nonsalient trials")
```
### 6. Block Analysis

```{r include=FALSE}
Exp6agg_B_fo <- aggregate(data = Exp6data, RT_ifo~participant+Validity+Saliency+BlockCount, subset = (Condition == "test"), mean)

Exp6agg_B_fo <- Exp6agg_B_fo %>%
  mutate(BlockMain = ifelse(BlockCount == "1" | BlockCount == "2",1,2))

Exp6agg_B1 <- Exp6agg_B_fo %>% subset(BlockMain == 1)
Exp6agg_B2 <-  Exp6agg_B_fo %>% subset(BlockMain == 2)
Exp6agg_B2 <- Exp6agg_B2 %>%
  filter(participant %notin% c(22,23,33,45,50,51))

table(Exp6agg_B2$participant)
table(Exp6agg_B1$Saliency,Exp6agg_B1$Validity)
table(Exp6agg_B_fo$BlockCount,Exp6agg_B_fo$Validity,Exp6agg_B_fo$Saliency)
table(Exp6agg_B_fo$BlockMain,Exp6agg_B_fo$Validity,Exp6agg_B_fo$Saliency)

aov_b1_fo <- aov(RT_ifo~(Validity*Saliency*BlockMain)+Error(participant/(Validity*Saliency*BlockMain)), data = Exp6agg_B_fo)
summary(aov_b_fo)

##EzANOVa not working because of unbalanced data
anova_t_block1 <- ezANOVA(data = Exp6agg_B1,
        dv = RT_ifo,
        wid = participant,
        within = .(Saliency,Validity),
        detailed = TRUE)
panderOptions('table.split.table',300)
pander(anova_t_block1, style = 'rmarkdown', caption = "ANOVA results: using IES(outliers)", split.table = "Inf", missing = NA)

anova_t_block2 <- ezANOVA(data = Exp6agg_B2,
        dv = RT_ifo,
        wid = participant,
        within = .(Saliency,Validity),
        detailed = TRUE)
panderOptions('table.split.table',300)
pander(anova_t_block2, style = 'rmarkdown', caption = "ANOVA results: using IES(outliers)", split.table = "Inf", missing = NA)


ezPlot(data = Exp6agg_B2,
        dv = RT_ifo,
        wid = participant,
        within = .(Saliency,Validity),x=Saliency,split=Validity,do_bars = FALSE)


ezPlot(data = Exp6agg_B1,
        dv = RT_ifo,
        wid = participant,
        within = .(Saliency,Validity),x=Saliency,split=Validity,do_bars = FALSE)
### Mutlilevel analysis

#null model
interceptOnly <- gls(RT_ifo~1, 
                     data=Exp6agg_B_fo,
                     method = "ML",
                     na.action= "na.omit")

summary(interceptOnly)

#within particpant
randomIntercept<-lmer(RT_ifo~1 + (1|participant), 
             data=Exp6agg_B_fo, 
             REML=F,
             na.action = "na.omit")
summary(randomIntercept)

#compare model with fixed vs random intercept
logLik(interceptOnly)*-2
logLik(randomIntercept)*-2

# adding validity as level 1 predictor
randomIntercept_p1<-lmer(RT_ifo~1+Validity + (1+Validity|participant), 
                         data=Exp6agg_B_fo, 
                         REML=F,
                         na.action = "na.omit")

summary(randomIntercept_p1)




#add saliency as level 1 predictor to model ####
randomIntercept_p2<-lmer(RT_ifo~1+Saliency + Validity + (1+Saliency + Validity|participant), 
                         data=Exp6agg_B_fo, 
                         REML=F,
                         na.action = "na.omit")


summary(randomIntercept_p2)
#values converge with SPSS output

#add BlockMain(2blocks) as level 1 predictor ####
randomIntercept_p3<-lmer(RT_ifo~1+Saliency + Validity + BlockMain + (1+Saliency + Validity+ BlockMain|participant), 
                         data=Exp6agg_B_fo, 
                         REML=F,
                         na.action = "na.omit")


summary(randomIntercept_p3)



  #adding interaction to model ####
  randomIntercept_p4<-lmer(RT_ifo~ 1+Saliency*Validity*BlockMain+ (1+Validity*Saliency*BlockMain|participant), 
                           data=Exp6agg_B_fo, 
                           REML=F,
                           na.action = "na.omit")
  
  summary(randomIntercept_p4)
  
  #compare  models
  anova(randomIntercept_p1, randomIntercept_p2)
  
  #comparing only intercept model with interaction
 anova(randomIntercept, randomIntercept_p4)


  
  #model comparisons ####
  #random slope, random intercept vs. fixed slope, random intercept
  randomIntercept_p5<-lmer(RT_ifo~1+ Validity*Saliency*BlockMain + (1|participant), 
                           data=Exp6agg_B_fo, 
                           REML=F,
                           na.action = "na.omit")
  
  summary(randomIntercept_p5)
  anova(randomIntercept_p4, randomIntercept_p5)  
  #random slope & random intercept model has better fit than random intercept & fixed slope model.  

```





### 7. Previous Occurence Analysis

Computing a new column that contains the last time/number of trials ago the previous occurence occured.

```{r prevocc}

Exp6data <- Exp6data%>%select(Condition, SalD,NSalD,Saliency,Validity, everything())

###first is to find out the trials where the previous occurence wa the immediate previous one
Exp6data$Distance <- NA
Exp6data <- Exp6data%>%select(Distance,ACC_trials,everything())
Exp6data <- Exp6data%>%
  mutate(Distance = ifelse((lag(Condition,1)=="test" | lag(Condition,1) == "learn")& 
              (lag(SalD,1)== SalD|lag(NSalD,1)==NSalD) &
                            lag(participant,1)==participant &
                            lag(ACC_trials,1)== 1, 1, Distance))

#The number of immediate previous occurences
pander(table(Exp6data$Distance), style = 'rmarkdown', caption = "Table showing the number of immediate previous occurence")

## Now to look at other distances of the last occurrence beyond the immediately preceding one
lagvalue <- 2:30

for(j in lagvalue){
  Exp6data <- Exp6data %>% 
    mutate(Distance = ifelse((lag(Condition,j)=="learn"|lag(Condition,j)=="test") &                     (lag(SalD,j)==SalD|lag(NSalD,j)==NSalD) & lag(participant,j)==participant & lag(ACC_trials,j)== 1 & is.na(Distance)==TRUE, j, Distance))
}

pander(table(Exp6data$Distance), style = 'rmarkdown', caption = "Table showing the number of total previous occurences and how far each of them are")

#ANOVA
# Exp6Dist_agg <- aggregate(data = Exp6data, RT_io~participant+Validity+Saliency+Distance, subset = (Distance <=12),mean)
# Exp6Dist_agg$Distance <- as.factor(Exp6Dist_agg$Distance)
# anova_Dist <- ezANOVA(data = Exp6Dist_agg,
#                       dv = RT_io,
#                       wid = .(participant),
#                       within = .(Saliency,Validity,Distance),
#                       detailed = TRUE)
# table(Exp6Dist_agg$Distance)
# pander()
```
### Previous Response

Coding what the previous Response was, whether it was the same or different

```{r}
Exp6data$ResponseType <- NA

Rmlag <- 1:30
for(k in Rmlag){
Exp6data <- Exp6data %>% 
  mutate(ResponseType = ifelse((lag(Condition,k)=="learn" | lag(Condition,k)=="test") &          (lag(SalD,k)==SalD|lag(NSalD,k)==NSalD) & lag(participant,k)==participant & lag(CorrectAnswer,k)== CorrectAnswer & is.na(ResponseType)==TRUE, "RR", ifelse((lag(Condition,k)=="learn"|lag(Condition,k)=="test") & (lag(SalD,k)==SalD|lag(NSalD,k)==NSalD)& lag(participant,k)==participant & lag(CorrectAnswer,k)!= CorrectAnswer & is.na(ResponseType)==TRUE, "RC", ResponseType)))
}

pander(table(Exp6data$ResponseType),style = 'rmarkdown', caption = "Total number of RRs and RCs")

Exp6data <- Exp6data%>%select(ResponseType, everything())
```



### checking for overshadowing in binding trials

```{r overSRB}
Exp6data$OvershadowSRB <- NA
Exp6data <- Exp6data%>%select(OvershadowSRB, everything())
Exp6data <- Exp6data %>%
  mutate(OvershadowSRB = ifelse((Condition == "test" & lag(Condition,1) == "learn") &
           lag(SalD,1)== SalD & lag(participant,1)==participant & lag(ACC_trials,1)== 1, 1,OvershadowSRB))

Exp6data <- Exp6data %>%
  mutate(OvershadowSRB = ifelse((Condition == "test" & lag(Condition,1) == "learn") &
           lag(NSalD,1)== NSalD & lag(participant,1)==participant & lag(ACC_trials,1)== 1 & is.na(OvershadowSRB) == TRUE,2,OvershadowSRB))

##including third category to check if there is a difference when neither repeats
# Exp6data <- Exp6data %>%
#   mutate(OvershadowSRB = ifelse((Condition == "test" & lag(Condition,1) == "learn") &
#            lag(participant,1)==participant & lag(ACC_trials,1)== 1 & is.na(OvershadowSRB) == TRUE,3,OvershadowSRB))
           
table(Exp6data$OvershadowSRB, Exp6data$Distance)  
Exp6data<- Exp6data%>%select(CorrectAnswer, everything())
##creating a dataframe that has only Binding trials preceding with learn 
Exp6_OverSRB <- Exp6data %>%
  subset(OvershadowSRB %in% c('1','2'))

Exp6_OverSRB<- Exp6_OverSRB%>%select(CorrectAnswer, everything())
table(Exp6_OverSRB$OvershadowSRB)
table(Exp6_OverSRB$Distance)
```

#### ANOVA: interaction between validity and Saliency for binding trials

```{r}
Exp6overSRB_Agg <- aggregate(Exp6_OverSRB[,c("RT_ifo","ErrorRate")], by = list(participant=Exp6_OverSRB$participant,
                                                                                      OvershadowSRB = Exp6_OverSRB$OvershadowSRB,
                                                                                      ResponseType = Exp6_OverSRB$ResponseType), mean, na.rm = TRUE)


Exp6overSRB_Agg$OvershadowSRB <- as.factor(Exp6overSRB_Agg$OvershadowSRB)
Exp6overSRB_Agg$IES <- Exp6overSRB_Agg$RT_ifo/(1-Exp6overSRB_Agg$ErrorRate)
anova_t_SRB<- ezANOVA(data = Exp6overSRB_Agg,
        dv = RT_ifo,
        wid = participant,
        within = .(OvershadowSRB,ResponseType),
        detailed = TRUE)
panderOptions('table.split.table',300)
pander(anova_t_SRB, style = 'rmarkdown', caption = "ANOVA results: using IES", split.table = "Inf", missing = NA)
anova_ER_SRB<- ezANOVA(data = Exp6overSRB_Agg,
        dv = ErrorRate,
        wid = participant,
        within = .(ResponseType,OvershadowSRB),
        detailed = TRUE)
panderOptions('table.split.table',300)
pander(anova_ER_SRB, style = 'rmarkdown', caption = "ANOVA results: using IES", split.table = "Inf", missing = NA)



ezPlot(data = Exp6overSRB_Agg,
        dv = RT_ifo,
        wid = participant,
        within = .(OvershadowSRB,ResponseType),do_bars = FALSE,x=ResponseType,split = OvershadowSRB)
       +theme_classic()+ylim(550,600)

t.test(data =Exp6overSRB_Agg, RT_io~ResponseType, subset = (OvershadowSRB == 1),paired = TRUE)

t.test(data =Exp6overSRB_Agg, RT_io~ResponseType, subset = (OvershadowSRB == 2),paired = TRUE)


```


## Exploratory Analysis

This exploratory analyusis involves the factors of contingency awareness from the guessing trials and the awareness questionnaire responses

#### Contingency Awareness guessing trials

```{r prepCA, include=FALSE}
Exp6_CA <- Exp6_CA %>%
  select(-TargetResp_p.corr,-TargetResp_p.keys,-TargetResp_p.rt,-TargetResp.corr,-TargetResp.keys,-todebrief.rt,-Finalend.rt)
Exp6_CA$AwareResp.corr <- as.factor(Exp6_CA$AwareResp.corr)
Exp6_CA$AwareResp.keys <- as.character(Exp6_CA$AwareResp.keys)
Exp6_CA$Solution <- as.character(Exp6_CA$Solution)
Exp6_CA$CAResponse.corr <- ifelse(is.na(Exp6_CA$CAResponse.corr) == TRUE, Exp6_CA$CAResponse_2.corr,Exp6_CA$CAResponse.corr)


Exp6_CA$SalTotalAcc <- NA
Exp6_CA$NonSalTotalAcc <- NA

Exp6_CA <- Exp6_CA %>%
  mutate(SalTotalAcc = ifelse(Saliency == "Salient" & CAResponse.corr == 1, 1, 0))

Exp6_CA <- Exp6_CA %>%
  mutate(NonSalTotalAcc = ifelse(Saliency == "NonSalient" & CAResponse.corr == 1, 1, 0))

CA_Summary <- Exp6_CA %>%
  dplyr::group_by(participant) %>%
  dplyr::summarise(TotalCA_Acc = sum(CAResponse.corr, na.rm=TRUE),
                   MeanAcc = mean(CAResponse.corr, na.rm=TRUE),
                  SalAcc = sum(SalTotalAcc, na.rm = TRUE),
                  NonSalAcc = sum(NonSalTotalAcc, na.rm = TRUE))
CA_Summary$participant <- as.factor(CA_Summary$participant)
CA_Summary$MeanAcc <- 100*CA_Summary$MeanAcc


```

These plots show the overall accuracy of the participants in the guessing trials that were spread across the experiment.

```{r CA plot, echo=FALSE, message=FALSE}
ggplot(CA_Summary, aes(x=participant, y = MeanAcc))+
  geom_bar(stat = "identity", fill = "palegreen4")+
  theme_classic()+
  ggtitle("Accuracy of Awareness trials per participants")

ggplot(CA_Summary, aes(x = participant))+
  geom_bar(aes(y=SalAcc),stat = "identity",fill="coral2",group="SalAcc")+
  geom_bar(aes(y=NonSalAcc), stat = "identity",fill="cornflowerblue",group = "NonSalAcc",alpha = 0.5)+
  labs(x = "Participant", y = "TotalAcc_Sal+NonSal", fill = "legend")+
  scale_fill_manual(values = c("SalAcc", "NonSalAcc"))+
  ggtitle("Summary of Contingency Awareness scores split by Salient or non salient test trial")
```

### Awareness Questionnaire

The accuracy for the questions related to the salient letter are aggregated and given an overall score of 1 if they answered both the questions right and 0 if one or both are wrong.

```{r awareprep, include=FALSE}
Exp6_CA$AwareResp.corr <- as.numeric(Exp6_CA$AwareResp.corr)
AWarepp <- aggregate(data = Exp6_CA, AwareResp.corr~participant+AwareQ_loop.thisN,mean)
AWarepp$Dicho <- ifelse(AWarepp$AwareQ_loop.thisN == "2" & AWarepp$AwareResp.corr == 1 | AWarepp$AwareQ_loop.thisN == "3" & AWarepp$AwareResp.corr== "1",1,0)

pander(table(AWarepp$AwareQ_loop.thisN,AWarepp$AwareResp.corr), style = "rmarkdown", title = "Question number and the number of participants answering accurately (1) or not (0)")
# table(AWarepp$Dicho)

A_Summary <- AWarepp %>%
  dplyr::group_by(participant) %>%
  dplyr::summarise(SaliencyAware = sum(Dicho, na.rm=TRUE))

A_Summary$allSalAware <- ifelse(A_Summary$SaliencyAware == "2" ,1,0)
```

This variable (allSalAware) is then included as a factor in the main aggregate df containing the validity and saliency effect for test trials


It does not show any significant effect. The graph however looks like as if those who do not have awareness show a larger validity effect for salient trials compared to those who do not. This is shown in the table below

```{r awareanalysis, echo=FALSE, warning=FALSE, message=FALSE}
Exp6agg_A_fo <- merge(Exp6agg_fo,A_Summary,by="participant")
Exp6agg_A_o <- merge(Exp6agg_o,A_Summary,by="participant")

#anova
anova_VSA_fo <- ezANOVA(data = Exp6agg_A_fo,
        dv = RT_ifo,
        wid = participant,
        within = .(Saliency,Validity),
        between = .(allSalAware),
        detailed = TRUE)

pander(anova_VSA_fo, style = 'rmarkdown', caption = "ANOVA results with awareness: Farouts excluded",split.table = "Inf", missing = NA)
Exp6agg_A_fo$allSalAware <- as.factor(Exp6agg_A_fo$allSalAware)

ezPlot(data = Exp6agg_A_fo,
        dv = RT_ifo,
        wid = participant,
        within = .(Saliency,Validity),
       between = .(allSalAware),
        split = Validity, x=Saliency, row = allSalAware,levels =  list(PosMatch = list (new_order = c('Salient', 'NonSalient'))), do_bars = FALSE)+
        theme_classic()+ylim(550,620)+
        ggtitle("Mean RT for valid and \n invalid trials across saliency and among participants who have awareness vs those who do not")

mean_aware <- ezStats(data = Exp6agg_A_fo,
        dv = RT_ifo,
        wid = participant,
        within_full = .(Saliency,Validity),
        within = .(Saliency),
        between = .(allSalAware),
        diff=.(Validity),
        reverse_diff = TRUE)

pander(mean_aware, style = "rmarkdown", title = "Validity effect(invalid-valid) for participants with contingency awareness of salient letters")



##for outliers


anova_VSA_o <- ezANOVA(data = Exp6agg_A_o,
        dv = RT_io,
        wid = participant,
        within = .(Saliency,Validity),
        between = .(allSalAware),
        detailed = TRUE)

pander(anova_VSA_o, style = 'rmarkdown', caption = "ANOVA results with awareness: Outliers excluded",split.table = "Inf", missing = NA)
Exp6agg_A_fo$allSalAware <- as.factor(Exp6agg_A_o$allSalAware)

ezPlot(data = Exp6agg_A_o,
        dv = RT_io,
        wid = participant,
        within = .(Saliency,Validity),
       between = .(allSalAware),
        split = Validity, x=Saliency, row = allSalAware,levels =  list(PosMatch = list (new_order = c('Salient', 'NonSalient'))), do_bars = FALSE)+
        theme_classic()+ylim(500,600)+
        ggtitle("Mean RT for valid and \n invalid trials(outliers excluded) across saliency and among participants who have awareness vs those who do not")

mean_aware_o <- ezStats(data = Exp6agg_A_o,
        dv = RT_io,
        wid = participant,
        within_full = .(Saliency,Validity),
        within = .(Saliency),
        between = .(allSalAware),
        diff=.(Validity),
        reverse_diff = TRUE)

pander(mean_aware_o, style = "rmarkdown", title = "Validity effect(invalid-valid) (outliers excluded) for participants with contingency awareness of salient letters")

```

Now we split the data and only analyze participants with awareness. 

Here we see that none of the effects are significant anymore (which was also visually evident from the graph)

```{r onlyaware, echo=FALSE, warning=FALSE, message=FALSE}

Exp6onlyAware_agg <- subset(Exp6agg_A_fo,subset = allSalAware == 1)

anova_A_fo <- ezANOVA(data = Exp6onlyAware_agg,
        dv = RT_ifo,
        wid = participant,
        within = .(Saliency,Validity),
        
        # within = .(PosMatch),
        # diff=.(Validity),
        # reverse_diff = TRUE,
        detailed = TRUE)
pander(anova_A_fo, style = 'rmarkdown', caption = "ANOVA results: Farouts excluded for participants with awareness",split.table = "Inf", missing = NA)


ezPlot(data = Exp6onlyAware_agg,
        dv = RT_ifo,
        wid = participant,
        within = .(Saliency,Validity),
        # within = .(PosMatch),
        # diff=.(Validity),
        # reverse_diff = TRUE,
       split = Validity, x=Saliency,levels =  list(Saliency = list (new_order = c('Salient', 'NonSalient'))), do_bars = FALSE)+
theme_classic()



mean_onlyaware <- ezStats(data = Exp6onlyAware_agg,
        dv = RT_ifo,
        wid = participant,
        within_full = .(Saliency,Validity),
        within = .(Saliency),
        diff=.(Validity),
        reverse_diff = TRUE)

pander(mean_onlyaware, style = "rmarkdown", title = "Validity effect(invalid-valid) for participants with contingency awareness of salient letters")
```

But now since the graph for participants with no awareness seemed like to have a larger effect, I further analyzed data of only those without awareness
This also did not show a significant interaction

```{r no aware, echo=FALSE, message=FALSE, warning=FALSE}
Exp6noAware_agg <- subset(Exp6agg_A_fo,subset = allSalAware == 0)

anova_noA_fo <- ezANOVA(data = Exp6noAware_agg,
        dv = RT_ifo,
        wid = participant,
        within = .(Saliency,Validity),
        
        # within = .(PosMatch),
        # diff=.(Validity),
        # reverse_diff = TRUE,
        detailed = TRUE)
pander(anova_noA_fo, style = 'rmarkdown', caption = "ANOVA results: Farouts excluded for participants without awareness",split.table = "Inf", missing = NA)


ezPlot(data = Exp6noAware_agg,
        dv = RT_ifo,
        wid = participant,
        within = .(Saliency,Validity),
        # within = .(PosMatch),
        # diff=.(Validity),
        # reverse_diff = TRUE,
       split = Validity, x=Saliency,levels =  list(Saliency = list (new_order = c('Salient', 'NonSalient'))), do_bars = FALSE)+
theme_classic()



mean_noaware <- ezStats(data = Exp6noAware_agg,
        dv = RT_ifo,
        wid = participant,
        within_full = .(Saliency,Validity),
        within = .(Saliency),
        diff=.(Validity),
        reverse_diff = TRUE)

pander(mean_noaware, style = "rmarkdown", title = "Validity effect(invalid-valid) for participants without contingency awareness of salient letters")
```

